Cellular Automata and Computational Universality

### 2018-07-30 paper/paper.tex
Visualisation working

\usepackage[margin=1in]{geometry}

@@

\end{document}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}

@@

\section{Introduction}
    A cellular automaton is a discrete model of computation which consists of a
    finite collection of ``cells'', each in one of a finite number of states.
    The state of each of these cells may evolve over the discrete progression of
    time in discrete steps, and may do so according to a deterministic set of
    rules specifying the state to which each cell is to progress, taking into
    account the states of cells in its neighbourhood. Their inherently discrete
    nature allows for strong analogies to be made with digital computers, and
    gifts them the ability to simulate digital processes and the potential to
    solve problems in this area.

    Consider the cellular automaton defined by the simple rule:
    $$ a_{i}^{t+1} = a_{i-1}^{t} + a_{i+1}^{t} \mod{2} $$
    For any automaton, in each time step the rule is applied to all cells in the
    automaton instantaneously and simultaneously. In this case, our set of
    states is ${0,1}$, and for each cell we look at the cells immediately
    preceding and succeeding it: if exactly one of them is in state 1, then this
    cell will be in state 1 in the next time step. Otherwise it will be in state
    0.

\section{Examples}
\section{Applications}
\section{Computational Universality}
\section{Firing Squad Synchronization Problem}
\section{Majority Problem}
\section{}
\end{document}
